Delocalization of Eigenvectors in Random Matrices

### 2025-03-19 Draft.tex
margins up to S6 and the two papers

        \vspace{0.5cm}
                \begin{center}
    \Large{\textsc{Advised by Dr. Kevin Yang}}
    \end{center}
    \vspace{1cm}
        \includegraphics[scale=1.25]{harvard_logo.png}

@@

\begin{equation*}
G_{xy} = G_{xy}^{(x)} - G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)} =- G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)}\quad x\neq y
\end{equation*}
Lastly, let us derive the derivatives of the resolvent w.r.t. to the matrix entry $H_{ij}$ using the limit definition. Let us define the perturbed matrix $H' = H(H_{ij}, H_{ji}\mapsto H_{ij}+\epsilon , H_{ji}+\epsilon)$ at entries $H_{ij}, H_{ji}$, where $G' = (H'-z)^{-1}$ and let $\epsilon_{ij} = \mathbf{0}(0_{ij}, 0_{ij}\mapsto \epsilon, \epsilon)$ be the perturbed zero matrix and write it as $\mathbf{1}_{ij}$ when $\epsilon=1$. Observe then that by our matrix identities, we have: $$\partial_{H_{ij}}G(z)_{xy}=\lim_{\epsilon\rightarrow 0} \frac{G_{xy}'-G_{xy}}{\epsilon} = \lim_{\epsilon\rightarrow 0}\frac{\left[G'(H-H')G\right]_{xy}}{\epsilon} = -\lim_{\epsilon\rightarrow 0}\frac{\left[G'\epsilon_{ij}G\right]_{xy}}{\epsilon} = -[G'\mathbf{1}_{ij}G]_{xy} = -G_{xi}G_{jy}$$

 $$\partial_{H_{ij}}\overline{G(z)_{xy}}=\lim_{\epsilon\rightarrow 0} \frac{\overline{G(z)_{xy}'}-\overline{G(z)_{xy}}}{\epsilon} = \lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}(H^\intercal-H'^\intercal)\overline{G}\right]_{xy}}{\epsilon} = -\lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}\epsilon_{ji}\overline{G}\right]_{xy}}{\epsilon} = -[\overline{G'}\mathbf{1}_{ji}\overline{G}]_{xy} = -\overline{G_{xj}}\overline{G_{iy}}$$

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[blue, ->] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=47	] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{1, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}G_{xu}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)G_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (delta) to[out=250, in=200, loop] (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=20] (beta);
\draw[blue, ->] (x) to (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, ->] (gamma) to (y);
\draw[blue, ->] (alpha) to [bend right=28](gamma);
\end{tikzpicture}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{31, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}B_{u\gamma}S_{\gamma \delta}G_{\alpha \gamma}(G_{\delta\delta}-m)G_{\gamma y}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
\end{center}

@@

\end{tikzpicture}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{41, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} B_{u\gamma}S_{\gamma \delta}G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma\beta} S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
\end{center}
\noindent Here the logic is the same as above, namely, after eliminating the loop at $\delta$ and the edges $x\textcolor{red}{\rightarrow} y$, $\gamma\textcolor{blue}{\rightarrow} \beta$, and $\beta\textcolor{blue}{\rightarrow} \alpha$ we get a term $O(W^{-2}\eta_s^{-1})$. The remaining graph is of similar form to the first two with additional wavy lines that contribute only $O(1)$ at the end, i.e $\mathcal{G}_{41, s}\lesssim W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\subsubsection*{Size estimates for $\mathcal{G}_{12, s}$}
Following the regular vertex expansion, we have to now represent the subgraphs of the form $\mathcal{G}_{i2, s}=B_{u\gamma} S_{\gamma \delta} G_{x_i\delta} (G_{\gamma\gamma}-m)G_{\delta y_i} f(G)$, s.t. by applying the graphical representation we get: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (delta) at (4, 0) {$\delta$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (gamma) at (3, 1) {$\gamma$};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (x) to (delta);
\draw[blue, ->] (gamma) to [out=210, in=240, loop] (gamma);
\draw[blue, ->] (beta) to [bend right=30] (alpha);
\draw[red, ->] (x) to [bend left = 30] (alpha);
\draw[red, ->] (beta) to (y);
\end{tikzpicture}
\end{center}
\begin{equation*}
\mathcal{G}_{22, s} = 
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{x\alpha}} B_{u\gamma} S_{\gamma \delta} G_{x\delta} (G_{\gamma\gamma}-m)G_{\delta y}\overline{G_{\beta y}} S_{uv} B_{v\alpha} S_{\alpha\beta}G_{\beta\alpha}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
Here we cancel the loop at $\gamma$ and the directed edges $x\textcolor{red}{\rightarrow}\alpha$, $\beta\textcolor{red}{\rightarrow}y$ and $\beta\textcolor{blue}{\rightarrow}\alpha$. With this, we are again left with a term $O(W^{-2}\eta_s^{-1})$, s.t. after summing out the wavy lines using estimate $(5)$, we get the same bound:
$\mathcal{G}_{22, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (x) to (beta);
\draw[blue, ->] (beta) to [bend left=30] (alpha);
\draw[blue, ->] (gamma) to [out=40, in=70, loop] (gamma);
\draw[blue, ->] (alpha) to [bend right=30] (delta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\end{center}
\begin{equation*}
\mathcal{G}_{32, s} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}G_{x\beta} B_{u\gamma} S_{\gamma \delta} G_{\alpha \delta} (G_{\gamma\gamma}-m)G_{\delta y}S_{uv}B_{v\alpha}S_{\alpha\beta}G_{\beta \alpha} 
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
For this subgraph, we start by eliminating the loop at $\gamma$ and the edges $\beta\textcolor{blue}{\rightarrow}\alpha$, $\alpha\textcolor{blue}{\rightarrow}\delta$, and $x\textcolor{red}{\rightarrow}y$. This means that we have 5 instead of 4 terms per estimate $(2)$, i.e we get a combined term $O(W^{-5/2}\eta_s^{-5/4})$. With this, we have a similar subgraph remaining with a few extra wavy edges that will sum out to $O(1)$ per estimate 5, hence the total estimate will be equivalent to:
$\mathcal{G}_{32, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (gamma) to[out=180, in=200, loop] (gamma);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=20] (beta);
\draw[blue, ->] (delta) to (beta);
\draw[blue, ->] (x) to (delta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, ->] (alpha) to [bend left=30](y);
\end{tikzpicture}
\end{center}
\begin{equation*}
\mathcal{G}_{42, s} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}B_{u\gamma} S_{\gamma \delta}  G_{x\delta} (G_{\gamma \gamma}-m)G_{\delta \beta}S_{uv} B_{v\alpha} S_{\alpha \beta} G_{\beta \alpha} G_{\alpha y}
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
Here, we eliminate the loop at $\gamma$ and the edges $\delta\textcolor{blue}{\rightarrow}\beta$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $x\textcolor{red}{\rightarrow}y$, all contributing a term $O(W^{-1/2}\eta_s^{-1/4})$. By summing over $\beta\rightsquigarrow \alpha$ for an $O(1)$ term, we again have a bound that is equivalent to the previous ones, since all the wavy lines sum up to contribute $O(1)$. As such, we have a bound, equivalent to:
$\mathcal{G}_{42, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (beta) to[out=180, in=220, loop] (beta);
\draw[wavy] (alpha) to (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=30](gamma);
\draw[blue, ->] (x) to (gamma);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (alpha) to[bend left=20] (delta);
\end{tikzpicture}
\end{center}
\begin{equation*}
\mathcal{G}_{13, s}^{(2)} =  \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}S_{uv}B_{v\alpha}G_{\alpha\delta}G_{\gamma\alpha}S_{\alpha\beta}(G_{\beta\beta}-m)B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta y}
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
We start by eliminating the loop at $\beta$ and then the edges $x\textcolor{red}{\rightarrow}\gamma$, $\gamma\textcolor{blue}{\rightarrow}\alpha$, and $\alpha\textcolor{blue}{\rightarrow}\delta$, getting back $O(W^{-2}\eta_s^{-1})$ by estimate $(2)$. Observe that with this we have almost the same subgraph as before with an additional wavy line $\gamma\rightsquigarrow \delta$, i.e our estimate looks like: 
$\mathcal{G}_{13, s}^{(2)}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (delta) at (3, 0) {$\delta$};
\node (y) at (4, 0) {y};
\node (b) at (5, 0) {b};

@@

$$\mathcal{E}_t^{M, 1} = \int_0^t(t-s)^2S^{1/2}\Theta_t\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}\Theta_t+\int_0^t(t-s)S^{1/2}\Theta_t\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}+$$
$$+\int_0^t(t-s)S^{1/2}\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}\Theta_t+ \int_0^t2S^{1/2}\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2} =$$
$$= \mathcal{E}_t^{M, 11}+\mathcal{E}_t^{M, 12}+\mathcal{E}_t^{M, 13}+\mathcal{E}_t^{M, 14}$$
Now, instead of applying the BDG inequality to the entire term, we can bound the individual $\mathcal{E}_t^{M, 1i}$ entries:

@@

>>>>

        \vspace{0.5cm}
                \begin{center}
    \Large{\textsc{Advised by Dr. Kevin Yang}}
    \end{center}
    \vspace{0.5cm}
        \includegraphics[scale=1.25]{harvard_logo.png}

@@

\begin{equation*}
G_{xy} = G_{xy}^{(x)} - G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)} =- G_{xx}\sum_{k\neq x}H_{xk}G_{ky}^{(x)}\quad x\neq y
\end{equation*}
Lastly, let us derive the derivatives of the resolvent w.r.t. to the matrix entry $H_{ij}$ using the limit definition. Let us define the perturbed matrix $H' = H(H_{ij}\mapsto H_{ij}+\epsilon)$ at entry $H_{ij}$, where $G' = (H'-z)^{-1}$ and let $\epsilon_{ij} = \mathbf{0}(0_{ij}\mapsto \epsilon)$ be the perturbed zero matrix, which we can write as $\mathbf{1}_{ij}$ when $\epsilon=1$. By our matrix identities, we have: $$\partial_{H_{ij}}G(z)_{xy}=\lim_{\epsilon\rightarrow 0} \frac{G_{xy}'-G_{xy}}{\epsilon} = \lim_{\epsilon\rightarrow 0}\frac{\left[G'(H-H')G\right]_{xy}}{\epsilon} = -\lim_{\epsilon\rightarrow 0}\frac{\left[G'\epsilon_{ij}G\right]_{xy}}{\epsilon} = -[G'\mathbf{1}_{ij}G]_{xy} = -G_{xi}G_{jy}$$
\begin{equation*}
\partial_{H_{ij}}\overline{G(z)_{xy}}= \lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}(H^\intercal-H'^\intercal)\overline{G}\right]_{xy}}{\epsilon} =\\\\= -\lim_{\epsilon\rightarrow 0}\frac{\left[\overline{G'}\epsilon_{ji}\overline{G}\right]_{xy}}{\epsilon} = -[\overline{G'}\mathbf{1}_{ji}\overline{G}]_{xy} = -\overline{G_{xj}}\ \overline{G_{iy}}
\end{equation*}

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[blue, ->] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=47	] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\end{tikzpicture}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{1, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}G_{xu}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)G_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (delta) to[out=250, in=200, loop] (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=20] (beta);
\draw[blue, ->] (x) to (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, ->] (gamma) to (y);
\draw[blue, ->] (alpha) to [bend right=28](gamma);
\end{tikzpicture}
\begin{equation*}\scalebox{0.92}{$
\mathcal{G}_{31, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}B_{u\gamma}S_{\gamma \delta}G_{\alpha \gamma}(G_{\delta\delta}-m)G_{\gamma y}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
\end{center}

@@

\end{tikzpicture}
\begin{equation*}\scalebox{0.92}{$
\mathcal{G}_{41, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} B_{u\gamma}S_{\gamma \delta}G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma\beta} S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
\end{center}
\noindent Here the logic is the same as above, namely, after eliminating the loop at $\delta$ and the edges $x\textcolor{red}{\rightarrow} y$, $\gamma\textcolor{blue}{\rightarrow} \beta$, and $\beta\textcolor{blue}{\rightarrow} \alpha$ we get a term $O(W^{-2}\eta_s^{-1})$. The remaining graph is of similar form to the first two with additional wavy lines that contribute only $O(1)$ at the end, i.e $\mathcal{G}_{41, s}\lesssim W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\subsubsection*{Size estimates for $\mathcal{G}_{12, s}$}
Following the regular vertex expansion, we have to now represent each of the subgraphs that has the form $\mathcal{G}_{i2, s}=B_{u\gamma} S_{\gamma \delta} G_{x_i\delta} (G_{\gamma\gamma}-m)G_{\delta y_i} f(G)$. By applying the graphical representation we get: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (delta) at (4, 0) {$\delta$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (gamma) at (3, 1) {$\gamma$};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (x) to (delta);
\draw[blue, ->] (gamma) to [out=210, in=240, loop] (gamma);
\draw[blue, ->] (beta) to [bend right=30] (alpha);
\draw[red, ->] (x) to [bend left = 30] (alpha);
\draw[red, ->] (beta) to (y);
\end{tikzpicture}
\end{center}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{22, s} = 
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{x\alpha}} B_{u\gamma} S_{\gamma \delta} G_{x\delta} (G_{\gamma\gamma}-m)G_{\delta y}\overline{G_{\beta y}} S_{uv} B_{v\alpha} S_{\alpha\beta}G_{\beta\alpha}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
Here we cancel the loop at $\gamma$ and the directed edges $x\textcolor{red}{\rightarrow}\alpha$, $\beta\textcolor{red}{\rightarrow}y$ and $\beta\textcolor{blue}{\rightarrow}\alpha$. With this, we are again left with a term $O(W^{-2}\eta_s^{-1})$, s.t. after summing out the wavy lines using estimate $(5)$, we get the same bound:
$\mathcal{G}_{22, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (x) to (beta);
\draw[blue, ->] (beta) to [bend left=30] (alpha);
\draw[blue, ->] (gamma) to [out=40, in=70, loop] (gamma);
\draw[blue, ->] (alpha) to [bend right=30] (delta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\end{center}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{32, s} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}G_{x\beta} B_{u\gamma} S_{\gamma \delta} G_{\alpha \delta} (G_{\gamma\gamma}-m)G_{\delta y}S_{uv}B_{v\alpha}S_{\alpha\beta}G_{\beta \alpha} 
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
For this subgraph, we start by eliminating the loop at $\gamma$ and the edges $\beta\textcolor{blue}{\rightarrow}\alpha$, $\alpha\textcolor{blue}{\rightarrow}\delta$, and $x\textcolor{red}{\rightarrow}y$. This means that we have 5 instead of 4 terms per estimate $(2)$, i.e we get a combined term $O(W^{-5/2}\eta_s^{-5/4})$. With this, we have a similar subgraph remaining with a few extra wavy edges that will sum out to $O(1)$ per estimate 5, hence the total estimate will be equivalent to:
$\mathcal{G}_{32, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (gamma) to[out=180, in=200, loop] (gamma);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=20] (beta);
\draw[blue, ->] (delta) to (beta);
\draw[blue, ->] (x) to (delta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, ->] (alpha) to [bend left=30](y);
\end{tikzpicture}
\end{center}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{42, s} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}B_{u\gamma} S_{\gamma \delta}  G_{x\delta} (G_{\gamma \gamma}-m)G_{\delta \beta}S_{uv} B_{v\alpha} S_{\alpha \beta} G_{\beta \alpha} G_{\alpha y}
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
Here, we eliminate the loop at $\gamma$ and the edges $\delta\textcolor{blue}{\rightarrow}\beta$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $x\textcolor{red}{\rightarrow}y$, all contributing $O(W^{-1/2}\eta_s^{-1/4})$. By summing over $\beta\rightsquigarrow \alpha$ for an $O(1)$ term, we again have a bound that is equivalent to the previous ones, since all the wavy lines sum up to contribute $O(1)$. As such, we have a bound, equivalent to:
$\mathcal{G}_{42, s}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (delta) at (2, 0) {$\delta$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (gamma) to (u);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy](gamma) to (delta);
\draw[blue, ->] (beta) to[out=180, in=220, loop] (beta);
\draw[wavy] (alpha) to (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=30](gamma);
\draw[blue, ->] (x) to (gamma);
\draw[blue, ->] (delta) to (y);
\draw[blue, ->] (alpha) to[bend left=20] (delta);
\end{tikzpicture}
\end{center}
\begin{equation*}\scalebox{0.95}{$
\mathcal{G}_{13, s}^{(2)} =  \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}
\overline{G_{xy}}S_{uv}B_{v\alpha}G_{\alpha\delta}G_{\gamma\alpha}S_{\alpha\beta}(G_{\beta\beta}-m)B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta y}
\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}$}
\end{equation*}
We start by eliminating the loop at $\beta$ and then the edges $x\textcolor{red}{\rightarrow}\gamma$, $\gamma\textcolor{blue}{\rightarrow}\alpha$, and $\alpha\textcolor{blue}{\rightarrow}\delta$, getting back $O(W^{-2}\eta_s^{-1})$ by estimate $(2)$. Observe that with this we have almost the same subgraph as before with an additional wavy line $\gamma\rightsquigarrow \delta$, i.e our estimate looks like: 
$\mathcal{G}_{13, s}^{(2)}\lesssim W^{-2}\eta_s^{-1}\times $\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (delta) at (3, 0) {$\delta$};
\node (y) at (4, 0) {y};
\node (b) at (5, 0) {b};

@@

$$\mathcal{E}_t^{M, 1} = \int_0^t(t-s)^2S^{1/2}\Theta_t\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}\Theta_t+$$
$$+\int_0^t(t-s)S^{1/2}\Theta_t\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}+$$
$$+\int_0^t(t-s)S^{1/2}\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2}\Theta_t+$$
$$+ \int_0^t2S^{1/2}\left\{\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\right\}S^{1/2} =$$
$$= \mathcal{E}_t^{M, 11}+\mathcal{E}_t^{M, 12}+\mathcal{E}_t^{M, 13}+\mathcal{E}_t^{M, 14}$$
Now, instead of applying the BDG inequality to the entire term, we can bound the individual $\mathcal{E}_t^{M, 1i}$ entries:

@@

\bibitem{yauyin} H.-T. Yau and J. Yin. Delocalization of One-Dimensional Random Band Matrices. \textit{arxiv.2501.01718}, 2025.

\bibitem{twodim} S. Dubova, K. Yang, H.-T. Yau, J. Yin. Delocalization of Two-Dimensional Random Band Matrices. \textit{arxiv.2503.07606}, 2025.
